Proposed Solution

### 2016-01-29 motiv1.tex
one result

When the user tries to install MySQL, she needs to initiate the path for
log information generated by MySQL. A user put the following code in 
her MySQL configuration file:\\
\texttt{
 \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
Unfortunately, the log information cannot be correctly written.
Running \app on this configuration file returns:
\xxx{Mark, put results here}\\
This is the root-cause of this misconfiguration problem. 
The entry ``general\_log'' should be an integer, 
rather than string. In MySQL, there is another entry named
``general\_log\_file'' used to specify the log path.

>>>>

When the user tries to install MySQL, she needs to initiate the path for
log information generated by MySQL. A user put the following code in 
her MySQL configuration file:\\
\texttt{
 \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
Unfortunately, the log information cannot be correctly written.
Running \app on this configuration file returns:
\begin{verbatim}
TYPE ERR ("general_log[mysqld]",ConfigQType {cint = Config {p = 1.0}, cstring = Config {p = 0.0}, cfilepath = Config {p = 0.0}})
\end{verbatim}
This is the root-cause of this misconfiguration problem. 
The entry ``general\_log'' should be an integer, 
rather than string. In MySQL, there is another entry named
``general\_log\_file'' used to specify the log path.
